Distributional Trees and Forests

### 2017-11-30 pkg/disttree/inst/CMStatistics2017/slides_rain.Rnw
different introduction to application
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1787 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7dee437966faf1aaed07c41f532ec96595d9037e

\begin{document}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Task:
\begin{itemize}
\item Goal: Predict total precipitation amount.
\item Input: Numerical Weather Prediction (NWP) with gridsize ... .
\item 
\vspace{0.1cm}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Data:
\begin{itemize}
\item Daily observations from 95 stations: \\
24h precipitation sums from July of 28 years.
\item Numerical ensemble predictions of meteorological quantities\\
\vspace{0.1cm}
$\rightarrow$ Covariates:\\
\begin{itemize}
\item Total precipitation
\item Convective available potential energy
\item Downwards short wave radiation flux (``sunshine'')
\item Mean sea level pressure 
\item Mean sea level pressure difference
\item Preciptable water
\item 2m maximum temperature
\item Total column-integrated condensate
\item Temperature 
\item Temperature differences in altitude
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Application for one station:
\begin{itemize}
\item Learn forest model on data from 24 years.
\item Evaluate on 4 years.
\item 10 times 7-fold cross validation.
\item Compare to commonly used methods:\\
\begin{itemize}
\item Prespecified GAM
\item Boosted GAM
\item Ensemble Model Output Statistics (EMOS) 
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
%Task:
\begin{itemize}
\item Goal: Predict total precipitation amount.
\item Input: Numerical Weather Prediction (NWP).
\item Idea: Statistical Model with numerical predictions as covariates.
\item Data:
\begin{itemize}
\item 95 observation stations in Tyrol.
\item Daily 24h precipitation sums from July of 28 years (1985--2012).
\item Numerical ensemble predictions of meteorological quantities.
\end{itemize}
\item Distribution Assumption: $(\text{Total precipitation})^\frac{1}{1/6} \sim \textit{c}\matchcal{N}$
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Variable Selection:
\begin{itemize}
\item Complex terrain \rightarrow unknown influences.
\item 85 Covariates:\\
\begin{itemize}
\item Total precipitation
\item Convective available potential energy
\item Downwards short wave radiation flux (``sunshine'')
\item Mean sea level pressure 
\item Mean sea level pressure difference
\item Preciptable water
\item 2m maximum temperature
\item Total column-integrated condensate
\item Temperature 
\item Temperature differences in altitude
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
\frametitle{Probabilistic Forecasting of Precipitation}
\vspace*{0.2cm}
Application for one station:
\begin{itemize}
\item Learn forest model on data from 24 years.
\item Evaluate on 4 years.
\item 10 times 7-fold cross validation.
\item Compare to commonly used heteroscedastic censored Gaussian models:\\
\begin{itemize}
\item Prespecified GAM: variable selection based on meteorological expert knowledge.
\item Boosted GAM: automatic variable selection.
\item Ensemble Model Output Statistics (EMOS): linear predictors using only total precipitation predictions as covariates.
\end{itemize}
\end{itemize}
\end{frame}
